Investigating Determinism of Physics Engines for usage in CAV and V\&V simulations

### 2021-04-26 document/source/body.tex
slight change to A* in sources and case study

\subsection{Actor Navigation}
There is evidence to suggest actor navigation, typically pedestrians, could be a source of non-deterministic simulation behaviour~\cite{CARLABenchmark}. Unreal Engine is the underlying framework for the CARLA simulator which uses the A* search algorithm to find optimal paths for actor navigation~\cite{newton2016unreal}. The optimality and validity of A* solutions is only guaranteed if the environment is deterministic, and if not, then there are no guarantees that an execution of the same A* solution will lead to the same outcome across multiple runs.

@@

The tests used for the case study are listed in Table~\ref{TableOfExperiments}. They cover a range of interactions between actor types. 
%
Tests 1 \& 2 involve two vehicles meeting at a junction where they either do not collide (Test 1) and where they do collide (Test 2), thereby triggering an \textit{event hit} callback in the game engine. In both cases the trajectories of the vehicles are hard-coded to follow a set of waypoints spaced at $0.1$m intervals using a PID controller. 
%
In Test 3 a mixture of different actor types is introduced where two vehicles drive without collision and a pedestrian walks across the road at a crossing point. 
%
In Test 4 this pedestrian collides with one of the vehicles at the crossing, triggering an \textit{event hit} callback, see Fig~\ref{Test_a}. Similar to vehicles, pedestrians navigate via a set of regularly spaced waypoints at $0.1$m intervals using the A* algorithm which is the default controller for the CARLA pedestrian actors. Tests 5 \& 6 involve only pedestrians that either do not collide (Test 5) and that do collide (Test 6), see Fig.~\ref{Test_b}.

>>>>

\subsection{Actor Navigation}
% There is evidence to suggest actor navigation, typically pedestrians, could be a source of non-deterministic simulation behaviour~\cite{CARLABenchmark}. Unreal Engine is the underlying framework for the CARLA simulator which uses the A* search algorithm to find optimal paths for actor navigation~\cite{newton2016unreal}. 
%
In game engines, the A* search algorithm is often used for navigation to find optimal paths for actors. 
%
The optimality and validity of A* solutions is only guaranteed if the environment is deterministic, and if not, then there are no guarantees that an execution of the same A* solution will lead to the same outcome across multiple runs.

@@

The tests used for the case study are listed in Table~\ref{TableOfExperiments}. They cover a range of interactions between actor types. 
%
Tests 1 \& 2 involve two vehicles meeting at a junction where they either do not collide (Test 1) and where they do collide (Test 2), thereby triggering an \textit{event hit} callback in the game engine. In both cases the trajectories of the vehicles are hard-coded to follow a set of waypoints spaced at $0.1$m intervals using a PID controller. 
%
In Test 3 a mixture of different actor types is introduced where two vehicles drive without collision and a pedestrian walks across the road at a crossing point.

Similar to vehicles, pedestrian actors navigate via a set of regularly spaced waypoints at $0.1$m intervals using the A* search algorithm which is the default method to find optimal paths for the CARLA pedestrian actors~\cite{newton2016unreal}. 
%
There is evidence to suggest that this actor navigation in Carla could be a source of non-deterministic simulation behaviour~\cite{CARLABenchmark}. 
%
This behaviour is explored in Test 4 where a pedestrian collides with one of the vehicles at the crossing, triggering an \textit{event hit} callback, see Fig~\ref{Test_a}.  
%
% Unreal Engine is the underlying framework for the CARLA simulator which uses the A* search algorithm to find optimal paths for actor navigation~\cite{newton2016unreal}.

Tests 5 \& 6 involve only pedestrians that either, do not collide (Test 5) and that do collide (Test 6), see Fig.~\ref{Test_b}.
